---
title: "2017 09 22 Cville Open Data Workshop Notes"
output: 
  html_notebook:
    toc: TRUE
    toc_float: TRUE
---

This notebook contains notes from the Open Data workshop and some tutorial 
information on the tools used during it.

## Packages

For the workshop, I will likely need to make use of the following packages. 

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(ggmap)
library(jsonlite)
library(httr)
```

## Testing ggmap

I want to create a test image of Charlottesville to play with during the 
workshop. Following the tutorial from the ggmap documentation, I can 
get the following from Google Maps.

### Downloading the map

First, I want to download the map.

```{r, message = FALSE}
cville_map <- get_googlemap("charlottesville virginia", zoom = 12, maptype = "roadmap")
```

### Creating the map

Next, I create the map using ggmap(). 

```{r, fig.width = 13}
ggmap(cville_map)
```

## Importing from ODI 

Now, I want to import some data from the Open Data Portal. To do this, I 
have gone onto the Open Data Portal and gotten the JSON API link for one of 
the data sets. 

```{r}
zone_parking_url <- "https://opendata.arcgis.com/datasets/fc3f283eb0124c9dad792f5fbe674397_37.geojson"
```

I can use this url to download the JSON directly into R using the FromJSON() 
function of jsonlite.

```{r}
zone_parking <- jsonlite::fromJSON(zone_parking_url)
```

We can now take a look at the structure of the imported JSON file.

```{r}
glimpse(zone_parking)
```

We can now turn the zone parking information into a data frame that we can use 
with the map.

```{r}
zone_parking_poly <- as_tibble(zone_parking$features$geometry)
```

### Importing the data using geojsonio

To get the files in as a true map file, I want to use the geojsonio package.

```{r}
library(geojsonio)
```

Now I can load in the map data. 

```{r}
zone_parking_geojson <- geojsonio::geojson_read(zone_parking_url, what = "sp")
```

What does the the imported map file look like? By making sure that geojson_read() 
is set to "sp" for Spatial class, I get a SpatialPolygonsDataFrame type 
object.

```{r}
glimpse(zone_parking_geojson)
```

## Manipulating geojson data for mapping

To map our zone parking file in ggmap (or ggplot2), I need to convert the 
Spatial Polygons Data Frame produced by geojson_read() into a normal data 
frame. This can be done with the tidy() function from the broom package. 

```{r}
zone_parking_df <- broom::tidy(zone_parking_geojson)
```

The data frame looks like: 

```{r}
glimpse(zone_parking_df)
```

## Mapping data

Now I can map the ODI data onto the map.

```{r}
cville_map %>% 
  ggmap() +
  geom_polygon(data = zone_parking_df, aes(x = long, y = lat, group = group), 
               color = "blue", 
               alpha = 0.4)
```

